Design and Implementation of Probabilistic Programming Language Anglican

### 2016-08-04 paper/paper.tex
minor

An Anglican program, or \textit{query}, is compiled into a Clojure
function. When inference is performed with a provided algorithm, this
produces a sequence of output values, or \textit{predicts}. Anglican
shares a common syntax with Clojure; Clojure functions can be called
from Anglican code and vice versa. A simple program in Anglican can
look like the following code:
\begin{lstlisting}[style=default]
(defquery models data
  "chooses a distribution
   which describes the data"
  (let [;; Guessing a distribution
        dist (sample (categorical
                       [[uniform-continuous 0 1]
                        [normal 0.5 1] 
                        [gamma 1 1]]))
        a (sample (gamma 1 1))
        b (sample (gamma 1 1))
        d (dist a b)]

@@

    ;; Predicting the distribution
    (predict :d (type d))
    (predict :a a) (predict :b b)))
\end{lstlisting}

>>>>

An Anglican program, or \textit{query}, is compiled into a Clojure
function. When inference is performed with a provided algorithm, this
produces a sequence of output values, or \textit{predicts}. Anglican
shares a common syntax with Clojure; Clojure functions can be called
from Anglican code and vice versa. A simple program in Anglican can
look like the following code:
\begin{lstlisting}[style=default]
(defquery model data
  "chooses a distribution which describes the data"
  (let [;; Guessing a distribution
        dist (sample (categorical
                       [[normal 0.5] 
                        [gamma 0.5]]))
        a (sample (gamma 1 1))
        b (sample (gamma 1 1))
        d (dist a b)]

@@

    ;; Predicting a, b and the distribution
    (predict :a a) 
    (predict :b b)
    (predict :d d)))
\end{lstlisting}
This query defines a probability distribution on predicted
variables, $\texttt{d} \in \{\texttt{normal},\texttt{gamma}\}$
for a distribution type, and $\texttt{a}$ and $\texttt{b}$ for
positive parameters for the type. Samples from this distribution 
can be obtained by running one of Anglican's inference algorithms
on the query.
